Caculating Bayesian R2

### 2025-03-26 ms/response_letter.qmd

---
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 12pt
format:
  pdf:
    keep-tex: true
    latex-clean: false
    pdf-engine: xelatex
    include-in-header:
      text: |
        \usepackage[default]{sourcesanspro}
        \usepackage{sourcecodepro}
        \usepackage{xcolor}
        \usepackage{mdframed}
        % Define blockquote colors
        \definecolor{blockquote-border}{RGB}{221,221,221}
        \definecolor{blockquote-text}{RGB}{119,119,119}
        % Define custom blockquote environment
        \newmdenv[
          rightline=false,
          bottomline=false,
          topline=false,
          linewidth=3pt,
          linecolor=blockquote-border,
          skipabove=\parskip,
          innerleftmargin=10pt,
          innerrightmargin=0pt,
          frametitlebackgroundcolor=gray!20
        ]{customblockquote}
        \renewenvironment{quote}
          {\begin{customblockquote}\color{blockquote-text}\ignorespaces}
          {\end{customblockquote}}
  html:
    theme: coderpro
    toc: true
    toc-depth: 2
    number-sections: true
    smooth-scroll: true
    standalone: true
    embed-resources: true
---

```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  cache = FALSE,
  fig.align = "center",
  fig.show = "hold"
)
```

Dear Editor,

We hereby resubmit the manuscript (JFR-D-25-00026), "Saturating allometric relationships reveal how wood density shapes global tree architecture".
We thank the handling editor and the reviewers for their careful attention to detail in our manuscript and for providing comments that have greatly improved the study.

Based on the comments, we have updated the manuscript to reflect the following:

1. **Improved content and clarity:**
We clarified the study’s main objective, added missing methodological details (e.g., wood density classification criteria and interpretation of $\Delta$LOOIC), and expanded the discussion to address potential confounding effects on allometric relationships.

2. **Enhanced presentation and formatting:**
We standardized the reporting of parameters, corrected figure labels, restructured supplementary tables for better readability, and revised the manuscript language to improve clarity and consistency.

We believe these revisions have strengthened the manuscript by clarifying our objectives, improving consistency and readability, and addressing key methodological concerns—thereby better highlighting the significance of our findings.

Below we provide detailed responses.
The editing history is recorded in a separate pdf file.

Sincerely,

Masatoshi Katabuchi

On behalf of the authors: Thi Duyen Nguyen

Corresponding author and contact information:
Key Laboratory of Tropical Forest Ecology, Xishuangbanna Tropical Botanical Garden, Chinese Academy of Sciences, Mengla, Yunnan 666303, China\
Email: katabuchi@xtbg.ac.cn; mattocci27@gmail.com

\newpage

# Responses

Please note that line numbers refer to ms_diff.pdf that contains editing history.
The word file has slightly different line numbers.

> Reviewer #3: The manuscript presents a comprehensive study on developing allometric models for estimating forest carbon biomass using global datasets and Bayesian hierarchical models. The authors highlighted the importance of saturating functions and wood density to improve allometric models without using two-step fitting approaches in previous studies (which seems problematic). Overall, the study provides valuable contributions to ecological theory and practical forestry applications. I have reviewed the entire manuscript very carefully and prepared below a detailed list of corrections and suggestions that will certainly improve the quality and make clearer the text.

Thank you very much for your positive and constructive feedback.

> 1) The technical information presented in the paper was interesting and worth reading.

Thank you for your kind remark.

> 2) Abstract is informative and it reflects the body of the paper.

We appreciate your positive feedback on the abstract.

> 3) The objectives must be modified for a better understanding of the reader.

Thank you for your suggestion.
We have revised the Introduction to clearly state the main objective of the study before presenting the specific questions (line XXX).

> 4) Line 366-369 & Table 2: In the sentence "In addition, the estimated exponent aligns closely with MST predictions for crown radius, supporting the selection of the power-law model for angiosperms, where the community-level exponent b is near the expected *2/3* ($b_{ang}$=0.625775 0.6168636,0.6345041, Table 2)" and the parameter estimates in Table 2, the values are not consistently presented. Check whole of the manuscript for a uniform presentation of the values.

We have standardized the presentation of all parameter estimates throughout the manuscript, including Table 2 and Table S6-8 and corresponding text.

> 5) Table 1: The table does not clearly explain how much of a difference in ΔLOOIC is considered significant between the two models.

We have revised the caption of Table 1 to clarify that a $\Delta$LOOIC greater than 4 suggests a meaningful difference in predictive performance (line XXX).

> 6) Figure S1: According to the supplementary materials section, the figure is incorrectly labeled Figure 1. It should be Figure S1.

We have corrected the figure label.

> 7) The reference section was informative. However, incorporate some latest references and arrange them according to the journal guidelines.

We have updated the references with recent publications, including xxx, and formatted them according to the journal guidelines.

> 8) Supplementary Table S6 is very congested and hard to read. Please revise for better understanding.

We have reformatted Supplementary Tables S6, S7, and S8 for improved readability and included detailed captions to aid interpretation.

> 9) A revision of the English is needed as some sentences aren't properly structured, and it's often difficult to grasp what the authors are saying.

We have revised the manuscript for language, grammar, and sentence structure to enhance clarity and improve overall readability.
For example, we revised lines XXX–YYY in the Discussion section to ensure sentence brevity and clarity.
Additionally, we updated the figure legends and table captions for greater clarity and carefully cross-checked all technical terms to maintain consistency throughout the text.

> Reviewer #5: Congratulations on a well-written and clear manuscript. Your approach to exploring allometric relationships between DBH, height, wood density, biomass, and crown radius is highly interesting and contributes significantly to the field. While I primarily focus on the data analysis section and found no major concerns, I would like to suggest a few minor corrections and discussion points.

Thank you so much for your encouraging and constructive feedback.

> 1) In Figure 3, the distinction between species with light and dense wood density is presented. However, the criteria used for this classification are not mentioned in the Materials and Methods section. Clarifying this would improve the transparency of your methodology.

Thank you for pointing this out.
We have added a description in the Methods section clarifying the classification criteria (line XXX).

> 2) Figure 4 appears to have a formatting issue, as the letters 'a' and 'd' are not displayed.

We have corrected the formatting issue in Figure 4.

> 3) It may be valuable to discuss the potential confounding effects of environmental factors on observed allometric correlations when considering wood density. Given intraspecific variation, wood density may not have a strong impact on those allometric relationships, since Fajardo et al. (2022) suggest that wood density is more closely linked to vessel anatomy than to tree architecture within the same species across different environments.

We agree with your point and have expanded the Discussion section to address potential environmental confounding effects.
We also cited Fajardo et al. (2022) to highlight less clear linkages between tree architecture and intraspecific variation in wood density  (line XXX).

> 4) I found the "Consequences for AGB Estimates" section particularly insightful.

Thank you for your positive feedback.

> 5) Pages 132-140 are blank, likely due to a formatting issue with the final table. The table appears to have fixed columns that prevent the complete display of cell information.

We have resolved the formatting issue that caused the blank pages in the supplementary file.

### 2025-03-26 ms/response_letter.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\usepackage[default]{sourcesanspro}
\usepackage{sourcecodepro}
\usepackage{xcolor}
\usepackage{mdframed}
% Define blockquote colors
\definecolor{blockquote-border}{RGB}{221,221,221}
\definecolor{blockquote-text}{RGB}{119,119,119}
% Define custom blockquote environment
\newmdenv[
  rightline=false,
  bottomline=false,
  topline=false,
  linewidth=3pt,
  linecolor=blockquote-border,
  skipabove=\parskip,
  innerleftmargin=10pt,
  innerrightmargin=0pt,
  frametitlebackgroundcolor=gray!20
]{customblockquote}
\renewenvironment{quote}
  {\begin{customblockquote}\color{blockquote-text}\ignorespaces}
  {\end{customblockquote}}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{2025-03-25}

\begin{document}

Dear Editor,

We hereby resubmit the manuscript (JFR-D-25-00026), ``Saturating
allometric relationships reveal how wood density shapes global tree
architecture''. We thank the handling editor and the reviewers for their
careful attention to detail in our manuscript and for providing comments
that have greatly improved the study.

Based on the comments, we have updated the manuscript to reflect the
following:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Improved content and clarity:} We clarified the study's main
  objective, added missing methodological details (e.g., wood density
  classification criteria and interpretation of \(\Delta\)LOOIC), and
  expanded the discussion to address potential confounding effects on
  allometric relationships.
\item
  \textbf{Enhanced presentation and formatting:} We standardized the
  reporting of parameters, corrected figure labels, restructured
  supplementary tables for better readability, and revised the
  manuscript language to improve clarity and consistency.
\end{enumerate}

We believe these revisions have strengthened the manuscript by
clarifying our objectives, improving consistency and readability, and
addressing key methodological concerns---thereby better highlighting the
significance of our findings.

Below we provide detailed responses. The editing history is recorded in
a separate pdf file.

Sincerely,

Masatoshi Katabuchi

On behalf of the authors: Thi Duyen Nguyen

Corresponding author and contact information: Key Laboratory of Tropical
Forest Ecology, Xishuangbanna Tropical Botanical Garden, Chinese Academy
of Sciences, Mengla, Yunnan 666303, China\\
Email: katabuchi@xtbg.ac.cn; mattocci27@gmail.com

\newpage

\section{Responses}\label{responses}

Please note that line numbers refer to ms\_diff.pdf that contains
editing history. The word file has slightly different line numbers.

\begin{quote}
Reviewer \#3: The manuscript presents a comprehensive study on
developing allometric models for estimating forest carbon biomass using
global datasets and Bayesian hierarchical models. The authors
highlighted the importance of saturating functions and wood density to
improve allometric models without using two-step fitting approaches in
previous studies (which seems problematic). Overall, the study provides
valuable contributions to ecological theory and practical forestry
applications. I have reviewed the entire manuscript very carefully and
prepared below a detailed list of corrections and suggestions that will
certainly improve the quality and make clearer the text.
\end{quote}

Thank you very much for your positive and constructive feedback.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  The technical information presented in the paper was interesting and
  worth reading.
\end{enumerate}
\end{quote}

Thank you for your kind remark.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Abstract is informative and it reflects the body of the paper.
\end{enumerate}
\end{quote}

We appreciate your positive feedback on the abstract.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
  The objectives must be modified for a better understanding of the
  reader.
\end{enumerate}
\end{quote}

Thank you for your suggestion. We have revised the Introduction to
clearly state the main objective of the study before presenting the
specific questions (line XXX).

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{3}
\tightlist
\item
  Line 366-369 \& Table 2: In the sentence ``In addition, the estimated
  exponent aligns closely with MST predictions for crown radius,
  supporting the selection of the power-law model for angiosperms, where
  the community-level exponent b is near the expected \emph{2/3}
  (\(b_{ang}\)=0.625775 0.6168636,0.6345041, Table 2)'' and the
  parameter estimates in Table 2, the values are not consistently
  presented. Check whole of the manuscript for a uniform presentation of
  the values.
\end{enumerate}
\end{quote}

We have standardized the presentation of all parameter estimates
throughout the manuscript, including Table 2 and Table S6-8 and
corresponding text.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{4}
\tightlist
\item
  Table 1: The table does not clearly explain how much of a difference
  in ΔLOOIC is considered significant between the two models.
\end{enumerate}
\end{quote}

We have revised the caption of Table 1 to clarify that a \(\Delta\)LOOIC
greater than 4 suggests a meaningful difference in predictive
performance (line XXX).

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{5}
\tightlist
\item
  Figure S1: According to the supplementary materials section, the
  figure is incorrectly labeled Figure 1. It should be Figure S1.
\end{enumerate}
\end{quote}

We have corrected the figure label.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{6}
\tightlist
\item
  The reference section was informative. However, incorporate some
  latest references and arrange them according to the journal
  guidelines.
\end{enumerate}
\end{quote}

We have updated the references with recent publications, including xxx,
and formatted them according to the journal guidelines.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{7}
\tightlist
\item
  Supplementary Table S6 is very congested and hard to read. Please
  revise for better understanding.
\end{enumerate}
\end{quote}

We have reformatted Supplementary Tables S6, S7, and S8 for improved
readability and included detailed captions to aid interpretation.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{8}
\tightlist
\item
  A revision of the English is needed as some sentences aren't properly
  structured, and it's often difficult to grasp what the authors are
  saying.
\end{enumerate}
\end{quote}

We have revised the manuscript for language, grammar, and sentence
structure to enhance clarity and improve overall readability.

\begin{quote}
Reviewer \#5: Congratulations on a well-written and clear manuscript.
Your approach to exploring allometric relationships between DBH, height,
wood density, biomass, and crown radius is highly interesting and
contributes significantly to the field. While I primarily focus on the
data analysis section and found no major concerns, I would like to
suggest a few minor corrections and discussion points.
\end{quote}

Thank you so much for your encouraging and constructive feedback.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  In Figure 3, the distinction between species with light and dense wood
  density is presented. However, the criteria used for this
  classification are not mentioned in the Materials and Methods section.
  Clarifying this would improve the transparency of your methodology.
\end{enumerate}
\end{quote}

Thank you for pointing this out. We have added a description in the
Methods section clarifying the classification criteria (line XXX).

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Figure 4 appears to have a formatting issue, as the letters `a' and
  `d' are not displayed.
\end{enumerate}
\end{quote}

We have corrected the formatting issue in Figure 4.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
  It may be valuable to discuss the potential confounding effects of
  environmental factors on observed allometric correlations when
  considering wood density. Given intraspecific variation, wood density
  may not have a strong impact on those allometric relationships, since
  Fajardo et al.~(2022) suggest that wood density is more closely linked
  to vessel anatomy than to tree architecture within the same species
  across different environments.
\end{enumerate}
\end{quote}

We agree with your point and have expanded the Discussion section to
address potential environmental confounding effects. We also cited
Fajardo et al.~(2022) to highlight less clear linkages between tree
architecture and intraspecific variation in wood density (line XXX).

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{3}
\tightlist
\item
  I found the ``Consequences for AGB Estimates'' section particularly
  insightful.
\end{enumerate}
\end{quote}

Thank you for your positive feedback.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{4}
\tightlist
\item
  Pages 132-140 are blank, likely due to a formatting issue with the
  final table. The table appears to have fixed columns that prevent the
  complete display of cell information.
\end{enumerate}
\end{quote}

We have resolved the formatting issue that caused the blank pages in the
supplementary file.

\end{document}

### 2025-03-26 docs/R2_new.qmd
Initial commit for tree-allo

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/workspaces/tree-allometry")
```

```{r global_options, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  cache = FALSE,
  fig.align = "center",
  fig.show = "hold"
)
```

```{r echo=FALSE}
library(targets)
library(tidyverse)
source("R/functions.R")
```

@@

## H
```{r}
stan_data_lr_h <- tar_read(stan_data_lr_h)
str(stan_data_lr_h)

# Without wood density
pl_nou_h <- tar_read(fit_lr2_draws_power_law1_nou_h)
pl_nou_h

gamma1_draws_pl_nou_h <- as.matrix(pl_nou_h[, "gamma[1]"])
gamma2_draws_pl_nou_h <- as.matrix(pl_nou_h[, "gamma[2]"])
sigma_draws_pl_nou_h <- as.matrix(pl_nou_h[, "sigma"])

num_sam_pl_nou_h <- nrow(gamma1_draws_pl_nou_h)
num_obs_pl_nou_h <- nrow(stan_data_lr_h$log_x)

log_y_pred_draws_pl_nou_h <- matrix(NA, nrow = num_sam_pl_nou_h, ncol = num_obs_pl_nou_h)

for (i in 1:num_sam_pl_nou_h) {
  log_y_pred_draws_pl_nou_h[i, ] <- gamma1_draws_pl_nou_h[i] + gamma2_draws_pl_nou_h[i] * stan_data_lr_h$log_x[, 2]
}

var_log_y_pred_pl_nou_h <- apply(log_y_pred_draws_pl_nou_h, 1, var)

var_res_pl_nou_h <- sigma_draws_pl_nou_h^2

bayes_R2_draws_pl_nou_h <- var_log_y_pred_pl_nou_h / (var_log_y_pred_pl_nou_h + var_res_pl_nou_h)

summary_bayes_R2_pl_nou_h <- summary(bayes_R2_draws_pl_nou_h)

summary_bayes_R2_pl_nou_h

# With wood density
pl_h <- tar_read(fit_lr2_draws_power_law1_h)
pl_h

gamma1_draws_pl_h <- as.matrix(pl_h[, "gamma[1,1]"])
gamma2_draws_pl_h <- as.matrix(pl_h[, "gamma[2,1]"])
sigma_draws_pl_h <- as.matrix(pl_h[, "sigma"])

num_sam_pl_h <- nrow(gamma1_draws_pl_h)
num_obs_pl_h <- nrow(stan_data_lr_h$log_x)

log_y_pred_draws_pl_h <- matrix(NA, nrow = num_sam_pl_h, ncol = num_obs_pl_h)

for (i in 1:num_sam_pl_h) {
  log_y_pred_draws_pl_h[i, ] <- gamma1_draws_pl_h[i] + gamma2_draws_pl_h[i] * stan_data_lr_h$log_x[, 2]
}

var_log_y_pred_pl_h <- apply(log_y_pred_draws_pl_h, 1, var)

var_res_pl_h <- sigma_draws_pl_h^2

bayes_R2_draws_pl_h <- var_log_y_pred_pl_h / (var_log_y_pred_pl_h + var_res_pl_h)

summary_bayes_R2_pl_h <- summary(bayes_R2_draws_pl_h)
summary_bayes_R2_pl_h
```

@@

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  cache = FALSE,
  fig.align = "center",
  fig.show = "hold"
)

```{r echo=FALSE}
library(targets)
library(tidyverse)
# source("R/functions.R")
```

@@

## H
```{r}
pl_nou_ang_h_sum <- tar_read(fit_lr_nou_summary_pl_ang_h)
pl_nou_ang_h_sum

beta_pl_nou_ang_h_sum <- pl_nou_ang_h_sum |> filter(grepl("beta", variable))
beta_pl_nou_ang_h_sum

### ANG
stan_data_lr_ang_h <- tar_read(stan_data_lr_ang_h)
str(stan_data_lr_ang_h)

# Without wood density
pl_nou_ang_h <- tar_read(fit_lr_nou_draws_pl_ang_h)
pl_nou_ang_h

# Get column names that match beta[1, ] and beta[2, ]
beta1_cols <- grep("^beta\\[1,\\d+\\]", colnames(pl_nou_ang_h), value = TRUE)
beta2_cols <- grep("^beta\\[2,\\d+\\]", colnames(pl_nou_ang_h), value = TRUE)

# Extract the beta[1, ] and beta[2, ] columns
beta1 <- as.matrix(pl_nou_ang_h[, beta1_cols])
beta2 <- as.matrix(pl_nou_ang_h[, beta2_cols])

dim(beta1)
dim(beta2)

# Assuming beta1 and beta2 are already extracted as matrices with dimensions (3000, 1214)
y_pred <- matrix(NA, nrow = nrow(stan_data_lr_ang_h$log_x), ncol = nrow(beta1))  # Empty matrix for predictions

# Loop over posterior draws and compute predicted log_y for each tree
for (i in 1:nrow(beta1)) {  # Loop over iterations (posterior draws)
  for (n in 1:stan_data_lr_ang_h$N) {       # Loop over trees
    # Extract the corresponding beta[1, jj[n]] and beta[2, jj[n]]
    beta_n <- c(beta1[i, stan_data_lr_ang_h$jj[n]], beta2[i, stan_data_lr_ang_h$jj[n]])

    # Multiply the log_x (tree-level predictors) by the corresponding beta values
    y_pred[n, i] <- stan_data_lr_ang_h$log_x[n, ] %*% beta_n  # Predicted log_y for each tree
  }
}

dim(y_pred)

@@

# H-DBH

## ANG

### Power-law
```{r}
stan_data_lr_ang_h <- tar_read(stan_data_lr_ang_h)
str(stan_data_lr_ang_h)

fit_lr_nou_draws_pl_ang_h <- tar_read(fit_lr_nou_draws_pl_ang_h)
fit_lr_nou_draws_pl_ang_h

r2_pl_nou_h_ang <- calculate_bayes_R2(
  stan_data_lr_ang_h,
  fit_lr_nou_draws_pl_ang_h,
  c("gamma[1]", "gamma[2]"),
  "lr"
)

summary(r2_pl_nou_h_ang)
```

### gMM
```{r}
stan_data_nlr_ang_h <- tar_read(stan_data_nlr_ang_h)
str(stan_data_nlr_ang_h)

fit_nlr_nou_draws_gmm_ang_h <- tar_read(fit_nlr_nou_draws_gmm_ang_h)
fit_nlr_nou_draws_gmm_ang_h

r2_gmm_nou_h_ang <- calculate_bayes_R2(
  stan_data_nlr_ang_h,
  fit_nlr_nou_draws_gmm_ang_h,
  c("gamma[1]", "gamma[2]", "gamma[3]"),
  "gmm"
)

summary(r2_gmm_nou_h_ang)
```

## Weibull

```{r}
stan_data_nlr_ang_h <- tar_read(stan_data_nlr_ang_h)
str(stan_data_nlr_ang_h)

fit_nlr_nou_draws_weibull_ang_h <- tar_read(fit_nlr_nou_draws_weibull_ang_h)
fit_nlr_nou_draws_weibull_ang_h

r2_weibull_nou_h_ang <- calculate_bayes_R2(
  stan_data_nlr_ang_h,
  fit_nlr_nou_draws_weibull_ang_h,
  c("gamma[1]", "gamma[2]", "gamma[3]"),
  "weibull"
)

summary(r2_weibull_nou_h_ang)
```

```{r}

```{r}

```{r}
